Enrich the datasets with new columns.

### 2020-11-26 inst/analysis/enrich_dataset.Rmd
Polishing preprocessing

r("undefined evals", nb_undefined$n)
r("percent undefined eval", ratio(nb_undefined$n, nb_eval_calls))
r("undefined eval expressions", nb_different_call_expr)
r("undefined out of corpus", nb_out_corpus$n)
r("undefined out of coprus percent", ratio(nb_out_corpus$n, nb_undefined$n))
```

>>>>

r("undefined evals", nb_undefined$n)
r("percent undefined eval", ratio(nb_undefined$n, nb_eval_calls))
r("undefined eval expressions", nb_different_call_expr)
r("undefined out of corpus", nb_out_corpus$n)
r("undefined out of corpus percent", ratio(nb_out_corpus$n, nb_undefined$n))
```
